On the replication of Sobol' sequences to estimate main effects of model inputs

### 2016-04-01 replicated_sobol.tex
filled subsection additive approach

\title{}

\author{Cl\'ementine Prieur, Elise Arnaud, Herv\'{e} Monod, Laurent Gilquin, Fred J. Hickernell, Llu\'{i}s Antoni Jim\'{e}nez Rugama}
\address{U. Josef Fourier, Illinois Institute of Technology}
\begin{abstract}
\end{abstract}

@@

\section{Problem Statement}
Denote by $\vx \in [0,1)^s$ a point with components $x_1,\dots,x_s$. We set $\mathcal{D}=\{1,\dots,s\}$. Let $u$ be a subset of $\mathcal{D}$, $-u$ its complement and $|u|$ its cardinality. $\vx_u$ represents a point in $[0,1)^u$ with components $x_j, j \in u$. Given two points $\vx$ and $\vx'$, we define the following hybrid point: 
\[\vz_u=(\vx_u:{\vx'}_{-u}), \text{ where: } \left\{
      \begin{aligned}
        z_j &= x_j, & \text{ if } j \in u\\
        z_j &= {x'}_j, & \text{ if } j \in -u\\
      \end{aligned}
    \right.  \]
Let $f$ be the symbol representing the numerical model considered. We assume $f \in \mathcal{L}^2[0,1]^s$. Denote by $\mu$ and $\sigma^2$ the mean and variance of $f$.
%These two quantities can be expressed as the following integrals:
%\[\mu= \frac{1}{2} \int_{[0,1)^{2d-1}}f(\vx)+f(\vx_u:{\vx'}_{-u}) d\vx d{\vx'}_{-u}, \]
%\[\sigma^2= \int_{[0,1)^{d}}f(\vx)^2 d\vx - \Big{(}\int_{[0,1)^{d}}f(\vx) d\vx\Big{)}^2 .\]
The uncertainty on $\vx$ is modeled by random variables such that $\vx \stackrel{iid}{\sim} \mathcal{U}[0,1)^s$. Recall the Hoeffding decomposition of $f$:
\begin{equation}
f(\vx)=\mu+\sum_{\substack{u \subseteq \{1,\dots,s\} \\ u \neq \emptyset}} f_u(\vx_u),
\label{anova}
\end{equation}
where: $\mu$ is a constant and $\forall \ u \subseteq \mathcal{D}, \ u \neq \emptyset, \ \forall \ j \in u: \int_{[0,1]} f_u(\vx_u) d{x_j}=0$.
Due to orthogonality, by taking the variance of each side in Equation \ref{anova} we obtain the following decomposition of the variance:
\[ \sigma^2 = \sum_{\substack{u \subseteq \{1,\dots,s\} \\ u \neq \emptyset}} \sigma_v^2.\]
The problem of interest is the estimation of the quantities:
\[\underline{\tau}_u^2 = \sum \limits_{v \subseteq u} \sigma_v^2, \qquad u \in \mathcal{D}.\]
These quantities correspond to the partial sensitivity Sobol' indices often found written in the literature in their normalized form: $\underline{\tau}_u^2/\sigma^2$. When, $|u|=1$, $\underline{\tau}_u^2$ corresponds to the first-order Sobol' index that evaluate the main effect of the variable $\vx_u$. Higher order indices evaluate higher order interactions between variables. In \cite{}, Owen proposed to use the following expression for $\underline{\tau}_u^2$:
\begin{equation}\label{first_order_indice}
\underline{\tau}_u^2  =\int_{[0,1)^{2s-1}}(f(\vx) - \mu) (f(\vx_u:{\vx'}_{-u})-\mu) d\vx d{\vx'}_{-u},
\end{equation}
taking $\mu$ as introduced in Janon \textit{et al.}:
\[\mu= \frac{1}{2} \int_{[0,1)^{2s-1}}f(\vx)+f(\vx_u:{\vx'}_{-u}) d\vx d{\vx'}_{-u}. \]
The natural way to estimate these two quantities is for $(\vx_i,\vx'_i) \stackrel{iid}{\sim} [0,1)^{2s}$ via:
\begin{align}
\widehat{\underline{\tau}_u^2} & = \frac{1}{n} \sum \limits_{i=1}^n (f(\vx_i) - \widehat{\mu}) (f(\vx_{i,u}:{\vx'}_{i,-u})-\widehat{\mu}),\label{first_order_indice_estimator}\\
\nonumber
\widehat{\mu} & = \frac{1}{2n} \sum \limits_{i=1}^n f(\vx_i) +f(\vx_{i,u}:{\vx'}_{i,-u}).
\end{align}

@@

An improvement to reduces this cost lies in the use of replicated designs. The notion of replicated designs was first introduced by McKay through the introduction of replicated Latin Hypercubes samples. Here, we define replicated designs in a wider framework:
\begin{defin}[Replicated designs]
Let $\mathcal{P}$ and $\mathcal{P}'$ be two points sets defined as follow:
%\[\arraycolsep=1.3pt
%D=\left(\begin{array}{ccccc}
%x_{1,1} & ... & x_{1,j} & ... & x_{1,s} \\
%\vdots &  & \vdots & & \vdots \\
%x_{i,1} & ... & x_{i,j} & ... & x_{i,s} \\
%\vdots &  & \vdots & & \vdots \\
%x_{n,1} & ... & x_{n,j} & ... & x_{n,s} \\
%\end{array} \right), \ D'=\left(\begin{array}{ccccc}
%{x'}_{1,1} & ... & {x'}_{1,j} & ... & {x'}_{1,s} \\
%\vdots &  & \vdots & & \vdots \\
%{x'}_{i,1} & ... & {x'}_{i,j} & ... & {x'}_{i,s} \\
%\vdots &  & \vdots & & \vdots \\
%{x'}_{n,1} & ... & {x'}_{n,j} & ... & {x'}_{n,s} \\
%\end{array} \right).
%\]
$\mathcal{P}=\{\vx_i\}_{i=0}^{n-1}$, $\mathcal{P}'=\{{\vx'}_i\}_{i=0}^{n-1}$, $(\vx_i,\vx'_i) \stackrel{iid}{\sim} [0,1)^{2s}$. Let $\mathcal{P}^u=\{\vx_{i,u}\}_{i=0}^{n-1}$ (resp. $\mathcal{P}'^u$), $u \subsetneq \mathcal{D}$, denote the subset of columns of $\mathcal{P}$ (resp. $\mathcal{P}'$) indexed by $u$. We say that $\mathcal{P}$ and $\mathcal{P}'$ are two replicated designs of order $r$ if:\\
$\forall \ u \subsetneq \mathcal{D}$ such that $|u|=r$, $\mathcal{P}^u$ and $\mathcal{P}'^u$ represent the same points set in $[0,1)^r$.
\end{defin}
The replication procedure introduced in \cite{•} allows to estimate all first-order Sobol' indices with two replicated designs of order $1$. In this procedure, the quantity $f(\vx_u:{\vx'}_{-u})$ is only evaluated $n$ times once for all $u$, resulting in a total of $2n$ evaluations of $f$. %Denote by $D$,$D'$ the two replicated designs of order $1$ required by the replication procedure, $D'$ is constructed from $D$ as follows:
%\[{x'}_{i,j}=x_{\pi_j(i),j}, \qquad \forall \ (i,j) \in \{1,\dots,n\} \times \{1,\dots,d\},\]
%where $\pi_1,\dots,\pi_d$ are $d$ permutations on $\{1,\dots,n\}$ selected randomly and independently.

Our objective here is to combine the use of Sobol' sequences with the replication method to iteratively estimate all quantities $\underline{\tau}_u^2, u \in \mathcal{D}$. This approach reduces to construct two replicated Sobol' sequences iteratively refined with new point sets. In this fashion, two approaches are considered: one multiplicative and one additive. In the next section, we provide some background on digital nets and sequences. The two approaches are detailed in Section \ref{sobol.seq.cons}.

@@

In this section we introduce a particular type of quasi-Monte Carlo points called digital nets to estimate the quantities $\eqref{first_order_indice}$. 
%, which will allow us to evaluate the integrand at points $\{\left(\vx_i,{\vx'}_{i,-u}\right)\}_{i=0}^{b^m}$ only one time to estimate all $d$ indices.
 The concept of $(t,m,s)$-net and $(t,s)$-sequence was first introduced and studied by Niederreiter in \cite{•}. $(t,m,s)$-nets are digital nets in $\cubes$ whose quality is measured by the parameter $t$ called $t$-value. %Because this parameter is the criterion we use to construct our new sequences, we provide the key definitions below.
 $(t,m,s)$-net and and $(t,s)$-sequence are strongly linked to the concept of star discrepancy \cite{.} and defined as follows:
\begin{defin}[$(t,m,s)-net$]
Let $\mathcal{A}$ be the set of all elementary intervals $A\in\cubes$ where $A=\prod_{i=1}^s [\alpha_jb^{-\gamma_j},(\alpha_j+1)b^{-\gamma_j})$, with integers $0\leq\gamma_j$ and $0\leq\alpha_j<b^{\gamma_j}$ for all $j=1,\dots,s$. For integers $s\geq 1$, $b\geq 2$, and $m\geq t\geq 0$, the points set $\mathcal{P}=\{\vx_i\}_{i=0}^{b^m-1}$, $\vx_i\in\cubes$, with $|\mathcal{P}|=b^m$, is a $(t,m,s)-net$ in base $b$ if:

@@

Digital nets are usually computed with square matrices $C_1^{\infty},\dots,C_s^{\infty}$ in $\mathbb{F}_b$ of size $\infty\times\infty$ often referred in the literature as generating matrices. However, to construct the first $b^m$ points, one only needs the knowledge of $C_1^m,\dots,C_s^m$. For each $i=0,\dots,b^m-1$, the points $\vx_i = (x_{i,1},\dots,x_{i,s})^\intercal$ of the sequence can be constructed as follows:
\begin{equation}
\label{dig.net.eq.}
(x_{i,j,1},x_{i,j,2},\dots)^\intercal = C_j^m (i_{0},\dots,i_{m-1})^\intercal,\qquad j= 1,\dots,s\, ,
\end{equation}
where $x_{i,j} = \sum_{k \geq 1}x_{i,j,k}b^{-k}$ is the radical inverse $b$-ary decomposition of point $x_{i,j}$ and $i = \sum_{k=0}^{m-1}i_kb^{k}$ is the $b$-ary decomposition of $i$. For $m' < m$ the matrices $C_j^{m'}$ are embedded in the upper left corners of matrices $C_j^{m}$. Thus, the digital nets possess an innate nested structure resulting from this embedding. That is $\mathcal{P}_{m'} \subset \mathcal{P}_m \subset \dots \subset \mathcal{P}_{\infty}$.

@@

We start by introducing some useful definitions for the rest of the paper. We note by $\vi=(i_{0},\dots,i_{m-1})^T$ the vector resulting from the binary decomposition $\eqref{dig.net.eq.}$ of integer $i$. We also note by $U_m(\mathbb{F}_2)$ the multiplicative group of all invertible triangular matrices of size $m\times m$ over the Galois field $\mathbb{F}_2$. Consider the following application:
\begin{equation*}
 \Diamond \colon \left\lbrace \begin{array}{ccccc} (\mathbb{F}_2)^m \times U_m(\mathbb{F}_2) & \to & (\mathbb{F}_2)^m \\
  (\vi,C) & \mapsto &  C . \vi \\
\end{array} \right.
\label{model}
\end{equation*}
The application $\Diamond$ consists in the operation carried on in Equation $\eqref{dig.net.eq.}$. It is easy to see that for $C \in U_m(\mathbb{F}_2)$ fixed, $\Diamond$ is a bijection of $(\mathbb{F}_2)^m$. As a results, applying $\Diamond$ for all $\vi \in (\mathbb{F}_2)^m$ with any generating matrix $C_j^m$ give the same points set. This leads to the following definition of replicated Sobol' sequences:
\begin{defin}
Let $C_j^m$, $C_{j'}^m$ be two generating matrices. The corresponding Sobol' sequences $\{\vx_i\}_{i=0}^{b^m-1}$ and $\{\vx'_i\}_{i=0}^{b^m-1}$ are two replicated designs of order $1$. Furthermore, the digital sequences $\{{\vx}_i\}_{i=0}^{\infty}$ and $\{{\vx'}_i\}_{i=0}^{\infty}$ are two replicated Sobol' sequence, that is for all $m \geq 0$, $\{{\vx}_i\}_{i=b^{m-1}}^{b^m-1}$ and $\{{\vx'}_i\}_{i=b^{m-1}}^{b^m-1}$ are two replicated designs of order $1$.
\end{defin}
In other worlds, Sobol' sequences are innate replicated designs of order $1$ possessing a nested structure.

@@

The best choice of primitive polynomials and directional numbers to generate good quality Sobol' sequences is deeply discussed in \cite{•}. We are going to take Kuo and Joe results to find  good \emph{replicated Sobol'} sequences.

Pairwise projections are already well optimized (see\cite[Table 2.1]{•}). Thus, our starting point will be using the $C_1,\dots,C_d$ found in \cite{•} to generate the sequence $\{{\vx}_i\}_{i\in\mathbb{N}_0}$. Hence, we will focus on finding the optimal $C'_{1},\dots,C'_{d}$ such that we minimize a $t$-value criteria (to specify, perhaps the max of all) over all $d$ sequences described in \eqref{ordered_sequence}.

@@

\subsection{Additive Approach}
%Notations:
%\begin{itemize}
%\item[.] $m$ denote the number of digits
%\item[.] $C_{m,1},\dots,C_{m,d}$: $d$ generator matrices of size $m \times m$ over the finite field $\mathcal{Z}_2$
%\item[.] $\vi$: base-$2$ representation of the integer $i$: $\vi=(i_1,\dots,i_m)^T$
%\item[.] $L_{m,l}$: nonsingular $m \times m$ lower triangular matrix over the finite field $\mathcal{Z}_2$
%\item[.] $\ve_{m,l}$: $m \times 1$ vector with elements from $\mathcal{Z}_2$
%\end{itemize}
%
%Denote by $X$ and $X'$ the two replicated designs of order $1$.
%A row of $X$ or $X'$ is a point in $[0,1]^d$. The symbol $x_i^j$ (resp. ${x'}_i^j$) corresponds to  the element of row $i$ and column $j$ of $X$ (resp. $X'$). The additive approach is described by Algorithm \ref{additive}. All operations are carried on the finite field $\mathcal{Z}_2$.
%\begin{algorithm}[!ht]
%
%\begin{center}
%\begin{minipage}{10cm}
%\begin{enumerate}
%\item[Step 1.] Instantiation: $X \leftarrow \emptyset$, $X' \leftarrow \emptyset$, $l \leftarrow 1$, $\widehat{\underline{\tau}_u^2}^{(0)} \leftarrow 0$.
%\item[Step 4.] $while$ ($!$ stopping criterion):
%\begin{enumerate}
%\item[4.1] Construct $L_{m,l}$ and $\ve_{m,l}$.
%\item[4.2] Augment both $X$ and $X'$:\\
%for $j=1,\dots,d$:\\
%for $i=1+2^{m+l-1},\dots,2^{m+l}$:
%\begin{flalign*}
%x_i^j & = C_{m,j} . \vi + \ve_{m,l} && \\
%{x'}_i^j & = L_{m,l} . (C_{m,j} . \vi +  \ve_{m,l})&&
%\end{flalign*}
%\item[4.3] For $u=1,\dots,d$: evaluate $\widehat{\underline{\tau}_u^2}^{(l)}.$ 
%\item[4.4.]  $l \leftarrow l+1.$
%\end{enumerate}
%\item[Step 5.] Return: $\widehat{\underline{\tau}_u^2}, \ u \in \{1,\dots,d\}.$ 
%\end{enumerate}
%\end{minipage}
%\end{center}
%\label{additive}
%\caption{Additive approach}
%\end{algorithm}

>>>>

\title{On the replication of Sobol' sequences to estimate main effects of model inputs}

\author{Cl\'ementine Prieur, Elise Arnaud, Herv\'{e} Monod, Laurent Gilquin, Fred J. Hickernell, Llu\'{i}s Antoni Jim\'{e}nez Rugama}
\address{University Grenoble Alpes, Illinois Institute of Technology, INRA Jouy-en-Josas}
%\begin{abstract}
%\end{abstract}

@@

\section{Problem Statement}
Denote by $\vx \in [0,1)^s$ a point with components $x_1,\dots,x_s$. We set $\mathcal{D}=\{1,\dots,s\}$. Let $u$ be a subset of $\mathcal{D}$, $-u$ its complement and $|u|$ its cardinality. $\vx_u$ represents a point in $[0,1)^u$ with components $x_j, j \in u$. Given two points $\vx$ and $\vx'$, we define the following hybrid point: 
\[\vz_u=(\vx_u:{\vx'}_{-u}), \text{ where: } \left\{
      \begin{aligned}
        z_j &= x_j, & \text{ if } j \in u\\
        z_j &= {x'}_j, & \text{ if } j \in -u\\
      \end{aligned}
    \right.  \]
Let $f$ be the symbol representing the numerical model considered. We assume $f \in \mathcal{L}^2[0,1]^s$. Denote by $\mu$ and $\sigma^2$ the mean and variance of $f$.
%These two quantities can be expressed as the following integrals:
%\[\mu= \frac{1}{2} \int_{[0,1)^{2d-1}}f(\vx)+f(\vx_u:{\vx'}_{-u}) d\vx d{\vx'}_{-u}, \]
%\[\sigma^2= \int_{[0,1)^{d}}f(\vx)^2 d\vx - \Big{(}\int_{[0,1)^{d}}f(\vx) d\vx\Big{)}^2 .\]
The uncertainty on $\vx$ is modeled by random variables such that $\vx \stackrel{iid}{\sim} \mathcal{U}[0,1)^s$. Recall the Hoeffding cite{hoeffding} decomposition of $f$:
\begin{equation}
f(\vx)=\mu+\sum_{\substack{u \subseteq \{1,\dots,s\} \\ u \neq \emptyset}} f_u(\vx_u),
\label{anova}
\end{equation}
where: $\mu$ is a constant and $\forall \ u \subseteq \mathcal{D}, \ u \neq \emptyset, \ \forall \ j \in u: \int_{[0,1]} f_u(\vx_u) d{x_j}=0$.
Due to orthogonality, by taking the variance of each side in Equation \ref{anova} we obtain the following decomposition of the variance:
\[ \sigma^2 = \sum_{\substack{u \subseteq \{1,\dots,s\} \\ u \neq \emptyset}} \sigma_v^2.\]
The problem of interest is the estimation of the quantities:
\[\underline{\tau}_u^2 = \sum \limits_{v \subseteq u} \sigma_v^2, \qquad u \in \mathcal{D}.\]
These quantities correspond to the partial sensitivity Sobol' indices \cite{sobol} often found written in the literature in their normalized form: $\underline{\tau}_u^2/\sigma^2$. When, $|u|=1$, $\underline{\tau}_u^2$ corresponds to the first-order Sobol' index that evaluate the main effect of the variable $\vx_u$. Higher order indices evaluate higher order interactions between variables. In \cite{owen}, Owen proposed to use the following expression for $\underline{\tau}_u^2$:
\begin{equation}\label{first_order_indice}
\underline{\tau}_u^2  =\int_{[0,1)^{2s-1}}(f(\vx) - \mu) (f(\vx_u:{\vx'}_{-u})-\mu) d\vx d{\vx'}_{-u},
\end{equation}
taking $\mu$ as introduced in \cite{monod,janon}:
\[\mu= \frac{1}{2} \int_{[0,1)^{2s-1}}f(\vx)+f(\vx_u:{\vx'}_{-u}) d\vx d{\vx'}_{-u}. \]
The natural way to estimate these two quantities is for $(\vx_i,\vx'_i) \stackrel{iid}{\sim} [0,1)^{2s}$ via:
\begin{align}
\widehat{\underline{\tau}_u^2} & = \frac{1}{n} \sum \limits_{i=1}^n (f(\vx_i) - \widehat{\mu}) (f(\vx_{i,u}:{\vx'}_{i,-u})-\widehat{\mu}),\label{first_order_indice_estimator}\\
\nonumber
\widehat{\mu} & = \frac{1}{2n} \sum \limits_{i=1}^n f(\vx_i) +f(\vx_{i,u}:{\vx'}_{i,-u}).
\end{align}

@@

An improvement to reduces this cost lies in the use of replicated designs. The notion of replicated designs was first introduced by McKay \cite{mckay} through the introduction of replicated Latin Hypercubes samples. Here, we define replicated designs in a wider framework:
\begin{defin}[Replicated designs]
Let $\mathcal{P}$ and $\mathcal{P}'$ be two points sets defined as follow:
%\[\arraycolsep=1.3pt
%D=\left(\begin{array}{ccccc}
%x_{1,1} & ... & x_{1,j} & ... & x_{1,s} \\
%\vdots &  & \vdots & & \vdots \\
%x_{i,1} & ... & x_{i,j} & ... & x_{i,s} \\
%\vdots &  & \vdots & & \vdots \\
%x_{n,1} & ... & x_{n,j} & ... & x_{n,s} \\
%\end{array} \right), \ D'=\left(\begin{array}{ccccc}
%{x'}_{1,1} & ... & {x'}_{1,j} & ... & {x'}_{1,s} \\
%\vdots &  & \vdots & & \vdots \\
%{x'}_{i,1} & ... & {x'}_{i,j} & ... & {x'}_{i,s} \\
%\vdots &  & \vdots & & \vdots \\
%{x'}_{n,1} & ... & {x'}_{n,j} & ... & {x'}_{n,s} \\
%\end{array} \right).
%\]
$\mathcal{P}=\{\vx_i\}_{i=0}^{n-1}$, $\mathcal{P}'=\{{\vx'}_i\}_{i=0}^{n-1}$, $(\vx_i,\vx'_i) \stackrel{iid}{\sim} [0,1)^{2s}$. Let $\mathcal{P}^u=\{\vx_{i,u}\}_{i=0}^{n-1}$ (resp. $\mathcal{P}'^u$), $u \subsetneq \mathcal{D}$, denote the subset of columns of $\mathcal{P}$ (resp. $\mathcal{P}'$) indexed by $u$. We say that $\mathcal{P}$ and $\mathcal{P}'$ are two replicated designs of order $r$ if:\\
$\forall \ u \subsetneq \mathcal{D}$ such that $|u|=r$, $\mathcal{P}^u$ and $\mathcal{P}'^u$ represent the same points set in $[0,1)^r$.
\end{defin}
The replication procedure introduced and studied in \cite{mara,tissot} allows to estimate all first-order Sobol' indices with two replicated designs of order $1$. In this procedure, the quantity $f(\vx_u:{\vx'}_{-u})$ is only evaluated $n$ times once for all $u$, resulting in a total of $2n$ evaluations of $f$. %Denote by $D$,$D'$ the two replicated designs of order $1$ required by the replication procedure, $D'$ is constructed from $D$ as follows:
%\[{x'}_{i,j}=x_{\pi_j(i),j}, \qquad \forall \ (i,j) \in \{1,\dots,n\} \times \{1,\dots,d\},\]
%where $\pi_1,\dots,\pi_d$ are $d$ permutations on $\{1,\dots,n\}$ selected randomly and independently.

Our objective here is to combine the use of Sobol' sequences \cite{sobolseq} with the replication method to iteratively estimate all quantities $\underline{\tau}_u^2, u \in \mathcal{D}$. This approach reduces to construct two replicated Sobol' sequences iteratively refined with new point sets. In this fashion, two approaches are considered: one multiplicative and one additive. In the next section, we provide some background on digital nets and sequences. The two approaches are detailed in Section \ref{sobol.seq.cons}.

@@

In this section we introduce a particular type of quasi-Monte Carlo points called digital nets to estimate the quantities $\eqref{first_order_indice}$. 
%, which will allow us to evaluate the integrand at points $\{\left(\vx_i,{\vx'}_{i,-u}\right)\}_{i=0}^{b^m}$ only one time to estimate all $d$ indices.
 The concept of $(t,m,s)$-net and $(t,s)$-sequence was first introduced and studied by Niederreiter in \cite{niederreiter}. $(t,m,s)$-nets are digital nets in $\cubes$ whose quality is measured by the parameter $t$ called $t$-value. %Because this parameter is the criterion we use to construct our new sequences, we provide the key definitions below.
 $(t,m,s)$-net and and $(t,s)$-sequence are strongly linked to the concept of star discrepancy \cite{star} and defined as follows:
\begin{defin}[$(t,m,s)-net$]
Let $\mathcal{A}$ be the set of all elementary intervals $A\in\cubes$ where $A=\prod_{i=1}^s [\alpha_jb^{-\gamma_j},(\alpha_j+1)b^{-\gamma_j})$, with integers $0\leq\gamma_j$ and $0\leq\alpha_j<b^{\gamma_j}$ for all $j=1,\dots,s$. For integers $s\geq 1$, $b\geq 2$, and $m\geq t\geq 0$, the points set $\mathcal{P}=\{\vx_i\}_{i=0}^{b^m-1}$, $\vx_i\in\cubes$, with $|\mathcal{P}|=b^m$, is a $(t,m,s)-net$ in base $b$ if:

@@

Digital nets are usually computed with square matrices $C_1^{\infty},\dots,C_s^{\infty}$ in $\mathbb{F}_b$ of size $\infty\times\infty$ often referred in the literature as generating matrices. However, to construct the first $b^m$ points, one only needs the knowledge of $C_1^m,\dots,C_s^m$. For each $i=0,\dots,b^m-1$, the points $\vx_i = (x_{i,1},\dots,x_{i,s})^\intercal$ of the sequence can be constructed as follows:
\begin{equation}
\label{dig.net.eq.}
(x_{i,j,1},x_{i,j,2},\dots)^\intercal = C_j^m (i_{0},\dots,i_{m-1})^\intercal,\qquad j= 1,\dots,s\, ,
\end{equation}
where $x_{i,j} = \sum_{k \geq 1}x_{i,j,k}b^{-k}$ is the radical inverse $b$-ary decomposition of point $x_{i,j}$ and $i = \sum_{k=0}^{m-1}i_kb^{k}$ is the $b$-ary decomposition of $i$. For $m' < m$ the matrices $C_j^{m'}$ are embedded in the upper left corners of matrices $C_j^{m}$. Thus, the digital nets possess an innate nested structure resulting from this embedding. %That is $\mathcal{P}_{m'} \subset \mathcal{P}_m \subset \dots \subset \mathcal{P}_{\infty}$.

@@

We start by introducing some useful definitions for the rest of the paper. We note by $\vi=(i_{0},\dots,i_{m-1})^\intercal$ the vector resulting from the binary decomposition $\eqref{dig.net.eq.}$ of integer $i$. We note by $\mathbb{N}_0$ the integer space. We also note by $U_m(\mathbb{F}_2)$ the multiplicative group of all invertible upper triangular matrices of size $m\times m$ over the Galois field $\mathbb{F}_2$. Consider the following application:
\begin{equation*}
 \Diamond \colon \left\lbrace \begin{array}{ccccc} (\mathbb{F}_2)^m \times U_m(\mathbb{F}_2) & \to & (\mathbb{F}_2)^m \\
  (\vi,C) & \mapsto &  C . \vi \\
\end{array} \right.
\end{equation*}
The application $\Diamond$ consists in the operation carried on in Equation $\eqref{dig.net.eq.}$. It is easy to see that for $C \in U_m(\mathbb{F}_2)$ fixed, $\Diamond$ is a bijection of $(\mathbb{F}_2)^m$. As a results, applying $\Diamond$ for all $\vi \in (\mathbb{F}_2)^m$ with any generating matrix $C_j^m$ give the same points set. This leads to the following definition of replicated Sobol' sequences:
\begin{defin}
Let $C_j^m$, $C_{j'}^m$ be two generating matrices. The corresponding Sobol' sequences $\{\vx_i\}_{i=0}^{b^m-1}$ and $\{\vx'_i\}_{i=0}^{b^m-1}$ are two replicated designs of order $1$. Furthermore, the digital sequences $\{{\vx}_i\}_{i\in\mathbb{N}_0}$ and $\{{\vx'}_i\}_{i\in\mathbb{N}_0}$ are two replicated Sobol' sequence, that is for all $m \geq 0$, $\{{\vx}_i\}_{i=b^{m-1}}^{b^m-1}$ and $\{{\vx'}_i\}_{i=b^{m-1}}^{b^m-1}$ are two replicated designs of order $1$.
\end{defin}
In other worlds, Sobol' sequences are innate replicated designs of order $1$ possessing a nested structure.

@@

The best choice of primitive polynomials and directional numbers to generate good quality Sobol' sequences is deeply discussed in \cite{kuo}. We are going to take Kuo and Joe results to find  good \emph{replicated Sobol'} sequences.

Pairwise projections are already well optimized (see\cite[Table 2.1]{kuo2}). Thus, our starting point will be using the $C_1,\dots,C_d$ found in \cite{kuo2} to generate the sequence $\{{\vx}_i\}_{i\in\mathbb{N}_0}$. Hence, we will focus on finding the optimal $C'_{1},\dots,C'_{d}$ such that we minimize a $t$-value criteria (to specify, perhaps the max of all) over all $d$ sequences described in \eqref{ordered_sequence}.

@@

\subsection{Additive Approach}

Denote by $\mathcal{P}$ and $\mathcal{P}'$ the two replicated designs iteratively refined with new points sets using the additive approach. These two designs possess a block structure:
$$\mathcal{P}= B_0 \cup B_1 \cup B_2 \dots $$
$$\mathcal{P}'= {B'}_0 \cup {B'}_1 \cup {B'}_2 \dots $$
We detail below the steps of the construction of these two designs.
\begin{enumerate}
\item[Step 1.] We start by fixing $m$ and choosing a set $C_1^{m},\dots,C_s^{m}$ of generating matrices to construct an initial Sobol' sequence $\{\vx_i\}_{i=0}^{2^m-1}$ of $2^m$ points. \\

\item[Step 2.] At step $l$ of the recursive estimation, $l \geq 0$, a new points set $B_l=\{\vx_i^{(l)}\}_{i=0}^{2^m-1}$ of $2^m$ points is added to $\mathcal{P}$. $B_l$ is obtained by applying a digital shift to the initial Sobol' sequence. The digital shift operation is applied as follows:

for each $i=0,\dots,2^m-1$, the points $\vx_i^{(l)} = (x_{i,1}^{(l)},\dots,x_{i,s}^{(l)})^\intercal$ is obtained by:
\begin{equation}
\label{dig.shift}
(x_{i,j,1}^{(l)},\dots,x_{i,j,m}^{(l)})^\intercal = C_j^m \vi^\intercal+\ve_j,\qquad j= 1,\dots,s\, ,
\end{equation}
where $ x_{i,j}^{(l)}=\sum_{k = 1}^mx_{i,j,k}^{(l)}2^{-k}$ and $\ve_j=(e_{j,{0}},\dots,e_{j,{m-1}})^\intercal \in (\mathbb{F}_2)^m$.\\

\item[Step 3.] Then, the points set ${B'}_l=\{{\vx'}_i^{(l)}\}_{i=0}^{2^m-1}$ is obtained from $B_l$ by applying Tezuka's i-binomial scrambling \cite{tezuka}. This operation consists in the following:

for each $i=0,\dots,2^m-1$, the points ${\vx'}_i^{(l)} = ({x'}_{i,1}^{(l)},\dots,{x'}_{i,s}^{(l)})^\intercal$ is obtained by:
\begin{equation}
\label{ibinom.scrambling}
({x'}_{i,j,1}^{(l)},\dots,{x'}_{i,j,m}^{(l)})^\intercal = L_j^m (x_{i,j,1}^{(l)},\dots,x_{i,j,m}^{(l)})^\intercal,
\end{equation}
where $ {x'}_{i,j}^{(l)}=\sum_{k = 1}^m{x'}_{i,j,k}^{(l)}2^{-k}$ and $L_j^m$ is an invertible lower triangular matrix of size $m \times m$ over the Galois field $\mathbb{F}_2$.\\

\item[Step 4.] The two blocks $B_l$ and ${B'}_l$ are then both randomised using a same Owen's scrambling \cite{owen.scrambl}

\item[Step 5.] $B_l$ and ${B'}_l$ are used to estimate all first-order indices $\underline{\tau}_u^2, u \in \mathcal{D}$.
\end{enumerate}
Steps $2$ to $5$ are iterated until a stopping criterion is reached. There is a finite choice for the vector $\ve_j$ and matrix $L_j^m$ respectively constructed in Steps $2$ and $3$. Once $m$ is fixed, one can build up to $2^m$ different $\ve_j$ and $2^{m(m-1)/2}$ different $L_j^m$. The choice of $m$ must take into account these limitations.

 At each step $l$, $B_l$ and ${B'}_l$ are two replicated designs of order $1$ thus enabling the estimation of all first-order indices. Denote by $K$ the step at which the recursive estimation stopped. The total cost of the additive approach to estimate all first-order indices equals $2 \times K \times 2^m$.

The additive approach is attractive due to the slow growing size of the two replicated designs $\mathcal{P}$ and $\mathcal{P}'$. At the opposite of the multiplicative approach, the main drawback is that $\mathcal{P}$ and $\mathcal{P}'$ does not possess the structure of a Sobol' sequence but each block $B_l$ (resp. $B'_l$) composing them does.

%Notations:
%\begin{itemize}
%\item[.] $m$ denote the number of digits
%\item[.] $C_{m,1},\dots,C_{m,d}$: $d$ generator matrices of size $m \times m$ over the finite field $\mathcal{Z}_2$
%\item[.] $\vi$: base-$2$ representation of the integer $i$: $\vi=(i_1,\dots,i_m)^T$
%\item[.] $L_{m,l}$: nonsingular $m \times m$ lower triangular matrix over the finite field $\mathcal{Z}_2$
%\item[.] $\ve_{m,l}$: $m \times 1$ vector with elements from $\mathcal{Z}_2$
%\end{itemize}
%
%Denote by $X$ and $X'$ the two replicated designs of order $1$.
%A row of $X$ or $X'$ is a point in $[0,1]^d$. The symbol $x_i^j$ (resp. ${x'}_i^j$) corresponds to  the element of row $i$ and column $j$ of $X$ (resp. $X'$). The additive approach is described by Algorithm \ref{additive}. All operations are carried on the finite field $\mathcal{Z}_2$.
%\begin{algorithm}[!ht]
%
%\begin{center}
%\begin{minipage}{10cm}
%\begin{enumerate}
%\item[Step 1.] Instantiation: $X \leftarrow \emptyset$, $X' \leftarrow \emptyset$, $l \leftarrow 1$, $\widehat{\underline{\tau}_u^2}^{(0)} \leftarrow 0$.
%\item[Step 4.] $while$ ($!$ stopping criterion):
%\begin{enumerate}
%\item[4.1] Construct $L_{m,l}$ and $\ve_{m,l}$.
%\item[4.2] Augment both $X$ and $X'$:\\
%for $j=1,\dots,d$:\\
%for $i=1+2^{m+l-1},\dots,2^{m+l}$:
%\begin{flalign*}
%x_i^j & = C_{m,j} . \vi + \ve_{m,l} && \\
%{x'}_i^j & = L_{m,l} . (C_{m,j} . \vi +  \ve_{m,l})&&
%\end{flalign*}
%\item[4.3] For $u=1,\dots,d$: evaluate $\widehat{\underline{\tau}_u^2}^{(l)}.$ 
%\item[4.4.]  $l \leftarrow l+1.$
%\end{enumerate}
%\item[Step 5.] Return: $\widehat{\underline{\tau}_u^2}, \ u \in \{1,\dots,d\}.$ 
%\end{enumerate}
%\end{minipage}
%\end{center}
%\label{additive}
%\caption{Additive approach}
%\end{algorithm}
\section*{References}
\bibliographystyle{elsarticle-num-names} 
\bibliography{bib}
